\documentclass{article}
\usepackage[a4paper, margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}

\title{Assignment 3}
\author{Om Shri Prasath, EE17B113}
\date{April 2020}
\begin{document}
\maketitle
\section*{Introduction}
\paragraph{}

The assignment consists of running the Alternating Least Squares (ALS) algorithm and Frequent Pattern Mining (FP Mining) algorithm using the Spark \textbf{mllib} Library on the given set of data.

\section*{ALS Algorithm}
\paragraph{}

 The data is given as a \textbf{'::'}-split data. It is split into its components and passed to the model, which gives the output and Test-RMSE.

 \paragraph{}

For different regularization parameters and iterations, we found the minimum RMSE for 20 iterations and regularization parameter of 0.1
For different train-test splits, we found the minimum RMSE for 0.9/0.1 split.

\paragraph{}

The outputs are present in \emph{ALS\_out\_1.txt} and \emph{ALS\_out\_2.txt}.

\section*{FP Growth Algorithm - 1}
\paragraph{}

The data is already given in a proper format to use. We split the data using \textbf{','}-data.

\paragraph{}

The maximum occuring pairs for a 0.04 \emph{min\_support} is :
\vspace{0.5em}

\begin{center}

    FreqItemset(items=[u'spaghetti', u'mineral water'], freq=448)\newline
    FreqItemset(items=[u'chocolate', u'mineral water'], freq=395)\newline
    FreqItemset(items=[u'eggs', u'mineral water'], freq=382) \newline
    FreqItemset(items=[u'milk', u'mineral water'], freq=360)\newline
    FreqItemset(items=[u'ground beef', u'mineral water'], freq=307)\newline
\end{center}

The output is present in \emph{fp1\_out.txt}.

\section*{FP Growth Algorithm - 2}

The data needs to be prepossessed for use in FP Growth. It is done by grouping the object via their \emph{Invoice Number} after removing NaN or empty rows. After that, it is run through the FP Growth Algorithm. 
\paragraph{}

The maximum occuring pairs (given as their ID's) for a 0.0236 \emph{min\_support} is :
\vspace{0.5em}


\paragraph{}

\begin{center}
    FreqItemset(items=[u'22386', u'85099B'], freq=554)\newline
    FreqItemset(items=[u'22697', u'22699'], freq=557)\newline
    FreqItemset(items=[u'22726', u'22727'], freq=536)\newline
    FreqItemset(items=[u'22384', u'20725'], freq=530) \newline
    FreqItemset(items=[u'22383', u'20725'], freq=526)\newline
\end{center}

The output is present in \emph{fp2\_out.txt} and the code for cleaning is in \emph{fp\_convert\_data.py}.

\end{document}
